MixEth: efficient, trustless coin mixing service for Ethereum

### 2018-12-13 article/shortpaper/main.tex
Added short paper version of the paper

There is no doubt that there exists a tremendous need for privacy overlays for Ethereum as new tools for transaction deanonymization are getting developed and used \cite{chan2017ethereum}. This need of the Ethereum community for privacy was spectacularly embodied in September, 2017 when for several days $68\%$ of all the transaction volume was controlled by a centralized coin mixing service \cite{hugemixer2017}.

@@

Eventhough (Ethereum) users and transactions can be deanonymized already on the network layer \cite{ethmacrofag2016}, we consider network anonymity an orthogonal problem to that of anonymity on the transaction ledger.

@@

\section{Background}
In this section we introduce the building bocks required to create our mixing protocol and MixEth, the trustless coin tumbler.
\subsection{Notations}
In most cases if it is possible we will stick to the notations used in \cite{meiklejohn2018mobius} for sake of uniformity. 
Let $[]$ denote the empty tuple. For a tuple $t=(x_1,\dots,x_n)$ we denote as $t[x_i]$ the value stored at $x_{i}$. The cardinality of a finite set $X$ is denoted as $|X|$. In the following let $\lambda \in \mathbb{N}$ be the security parameter and its unary representation is $1^{\lambda}$. If $x$ is uniformly randomly sampled from a set $A$ we write $x\stackrel{\$}{\leftarrow}A$. The symmetric group of degree $n$ is written as ${S}_n$. In a cyclic group $\mathbb{G}$, the standardized generator is denoted as $G$ and we use the additive notation. Secret keys and public keys are denoted as $sk$ and $pk$ respectively (or often times $s$ and $sG$), while the user the corresponding key belongs to is indicated in subscript. Let $PK_{i}$ denote the set of public keys belonging to receivers at a particular shuffling round $i$.

@@

\subsection{Verifiable shuffle}

Neff introduced the notion of verifiable shuffle \cite{neff2001verifiable}. It is a cryptographic protocol allowing a party to verifiably shuffle a sequence of $k$ modular integers. The output of the shuffle is another $k$ modular integers raised to the same secret exponent only known to the shuffler. The shuffler can generate a publicly verifiable zero-knowledge proof to convince the public that the shuffle was done correctly.

Neff's mathematical construct is extremely powerful, since it only relies on the intractability of the Decision Diffie-Hellman (DDH) problem. Therefore, Neff's verifiable shuffle can also be applied in groups over elliptic curves.

Verifiable shuffle can be used to shuffle a set of public keys, $PK=(s_{1}G,s_{2}G\dots,s_{k}G)$. Note that secret keys are not known to the shuffler.

\begin{enumerate}
	\item Shuffler commits to $C=cG$, publishes $$PK^*=(c(s_{\pi^{-1}(1)}G),c(s_{\pi^{-1}(2)}G),\dots,c({s_{\pi^{-1}(k)}}G))$$ where $\pi$ is a random permutation. Shuffler additionally computes and publishes a zero-knowledge proof about the correctness of the shuffle. This proof can be made non-interactive via the Fiat-Shamir heuristic. Let us call $C$ as the shuffling constant.
	\item Assuming the proof verifies users gain new public keys with respect to another generator element, namely $cG$.
\end{enumerate}

For verifying the proof one needs to compute $8k+5$ exponentiations, however later this result was ameliorated to $3,5k$ exponentiations by Bayer and Groth \cite{bayer2012efficient}.

So far verifiable shuffles were only applied in voting schemes, we argue that they are useful in trustless coin mixers as well. The key insight in order to be able to apply verifiable shuffles in a decentralized, computational-resource-constrained environment, for instance Ethereum smart contracts, is to dismiss the proof generation for the correctness of the shuffle, rather we request users to give more succints proofs for the incorrectness of the shuffle, if applies.

@@

In our security proofs we will be relying on the fact that ECDSA is \textit{existentially unforgeable} \cite{{fersch2016provable}}, i.e. no efficient adversary could forge a signature on any given message with non-negligible probability.

@@

EVM is quasi-Turing complete, since smart contract's code can not run indefinitely due to the so called \textit{gas mechanism}. In every transaction the sender needs to pay upfront for the execution of the contract's code. The computational complexity of a transaction is measured in gas, which can be bought for Ether on a price set by the transaction originator, so called gas price. Therefore the transaction fee is the gas cost multiplied by the gas price. One needs to specify a gas limit, meaning that they do not allow their transaction to burn more gas than the limit. If a transaction during execution runs out of gas, then all the state changes are reverted, while the transaction fee is paid to the miner. If there are gas left after successful execution, transaction originator is reimbursed. Additionally there exists a block gas limit, which limits the number of computational steps fitting in one block. Currently the block gas limit is cca. $\num[group-separator={,}]{8000000}$ gas. Naturally users of Ethereum are very much incentivized to minimize the gas cost of their transactions in order to spend as less as possible on transactions fees. Small gas costs are also crucial from a scalability point of view, since the less gas burnt for each transaction, the more transaction can fit into a single block.

@@

\subsubsection{Ethereum account abstraction}
Unfortunately, neither Möbius nor Miximus can be deployed on the present-day Ethereum. When users of the coin mixing contract, either Möbius or Miximus would like to withdraw their funds they can not do this from a fresh address, since it does not hold any ether. Since as of now only the sender of a transaction can pay for the gas fee, users can not withdraw their funds unless they ask someone to fund their fresh address.

Another solution for this problem is the Ethereum Improvement Proposal (EIP) 86 suggested by Nick Johnson and Vitalik Buterin \cite{buterin2017accounteip}. EIP86 permits receivers of a transaction paying the gas fee. This would certainly enable a functional Möbius and Miximus as well, since the tumbling contract could pay for the withdrawal transactions' gas fee, eliminating the previous workaround to unlinkably fund freshly mixed addresses. Additionally, EIP86 also allows contracts and accounts to define their own digital signature algorithms. This means that users are no longer required to sign transactions with Elliptic Curve Digital Signature Algorithm (ECDSA). Moreover if EIP86 or something similar is implemented, which is expected in 2019, MixEth is also made viable.

\section{Threat model}
\subsection{Participants and interactions}
In a decentralized tumbler, we have $3$ distinct entities: the tumbling smart contract, a set of senders and a set of receivers. A sender, whom we will call Alice, sends funds to the receiver, Bob, through the mixer contract in order to break direct links between their public keys. In all the following interactions and algorithms we assume that the public state of the tumbler is implicitly given as input. Interactions of these entities can be summarized as follows:

$tx\stackrel{\$}{\leftarrow}Deposit(sk_A,pk_B)$: The sender runs this algorithm to deposit a predefined amount of ether to the receiver's public key.

$0/1\leftarrow VerifyDeposit(tx)$: The tumbler contract checks the validity of senders' deposits.

$ProcessDeposit(tx)$: upon receiving a valid deposit transaction, the mixing contract updates its internal state accordingly.

Let $PK_{0}$ denote the set of public keys after the depositing period to be mixed. Furthermore let us set $C^{*}_{0}=G$, the standard generator point of the secp256k1 curve. Anyone is allowed to shuffle the public keys at most once by paying some deposit to the tumbler contract:

$PK_{i+1},C_{i+1}^{*}\stackrel{\$}{\leftarrow}Shuffle(PK_{i},C^{*}_{i},c_{i},\pi_{i})$. Let us call $C^{*}_{i}$ as the shuffling accumulated constant, which can be obtained by $C^{*}_{i+1}=c_{i}C^{*}_{i}$. The shuffling accumulated constant is needed for receivers to audit shuffling and to collect their funds at the end of the final shuffling period. The permutation $\pi$ and the secret multiplier $c_{i}$ from the new shuffling accumulated constant should be kept private after shuffling, otherwise it is trivial to track how public keys are shuffled. All the outputs of the $Shuffle$ algorithm are public and written into the tumbling contract.

$0\lor1\leftarrow 
ChallengeShuffle(PK_{i},C^{*}_{i},PK_{i-1},C^{*}_{i-1},pk_{B})$: receiver $B$ with public key $pk_{B}=s_{B}G$ can challenge an incorrect shuffle at the $i$th round by giving a Chaum-Pedersen zero-knowledge proof that the following tuple is DDH-tuples: $(C^{*}_{i-1}, s_{B}C^{*}_{i-1}, C^{*}_{i}, s_{B}C^{*}_{i})$. If the proof verifies and $s_{B}C^{*}_{i} \notin PK_{i}$, while $s_{B}C^{*}_{i-1} \in PK_{i-1}$, then the challenge is accepted, otherwise rejected. This proof and checks allow one to be certain that indeed the $i$th round is the first round in which the corresponding public key to $s_{B}$ is shuffled incorrectly.

$tx\stackrel{\$}{\leftarrow}WithdrawShufflingDeposit(sk_B)$: after a challenging period a shuffler can withdraw their shuffling deposit from the tumbler contract.

$0\lor1\leftarrow VerifyWitdhrawShufflingDeposit(pk_B)$: if there was no successful challenges against the shuffler, i.e. their deposit is not slashed, they can withdraw their shuffling deposit.

$tx\stackrel{\$}{\leftarrow}Withdraw(sk_B, C^{*}_{final})$: after the end of the shuffling period users are allowed to withdraw their funds. Note that here withdraw transactions will be signed with a modified version of ECDSA, where not the original generator element $G$ is used as generator rather $C^{*}_{final}$, the final shuffling accumulated constant.

$0/1\leftarrow VerifyWithdraw(tx)$: tumbler checks the validity of a recipient's withdrawal transaction.

$ProcessWithdraw(tx)$: upon receiving a valid withdrawal transaction, mixing contract updates its internal state accordingly.

\subsection{Security goals} \label{securitygoals}
We are aiming to achieve and prove the same notions of security as the ones defined in \cite{meiklejohn2018mobius}, namely anonymity, availability and theft prevention. These notions of anonymity, availability and theft prevention were introduced in \cite{meiklejohn2018mobius}, which are included in this section for sake of self-containedness.

@@

In the security definitions and games introduced by \cite{meiklejohn2018mobius} adversary $\adv$ might have access to the following oracles. CORR enables $\adv$ to corrupt a sender or receiver by learning the secret key of any party $l$ of their choice. Oracle access to AD or AW allow $\adv$ to deposit or withdraw respectively from tumbler session $j$. Furthermore $\adv$ might instruct honest senders or receivers to deposit or withdraw from tumbler session $j$ by using oracles HD and HW. In the following $C$ denotes the set of corrupted parties, while the list of honest deposits and withdrawals are denotes as $H_{d}$ and $H_{w}$ respectively The list of contract identifiers associated with distinct sessions is denoted as $tumblers$.

These oracles are formally defined as follows:

\begin{table}[H]
	\centering
	\begin{tabular}{cccc}    
		\begin{minipage}{6cm}
			\procedure{AD(tx,$j$)}{%
				b \leftarrow VerifyDeposit(tumblers[j],tx) \\
				if\ (b) \ ProcessDeposit(tumblers[j],tx) \\
				\pcreturn b  }
		\end{minipage}
		&
		\begin{minipage}{6cm}
			\procedure{AW(tx,$j$)}{%
				b \leftarrow VerifyWithdraw(tumblers[j],tx) \\
				if\ (b) \  ProcessWithdraw(tumblers[j],tx) \\
				\pcreturn b  }
		\end{minipage}
		&
		\begin{minipage}{4cm}
			\procedure{CORR($l$)}{%
				C=C.push(pk_{B_{l}}) \\
				\pcreturn sk_{B_l}}
		\end{minipage}
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{cc}   
\begin{minipage}{5cm}
	\procedure{HD($i$,$j$,$l$)}{%
		tx\stackrel{\$}{\leftarrow}Deposit(sk_{A_{i}},pk_{B_{l}})\\
		H_{d}=H_{d}.push(tx) \\
		ProcessDeposit(tumblers[j],tx)\\
		\pcreturn tx }
\end{minipage}
&
\begin{minipage}{5cm}
	\procedure{HW($j$,$l$)}{%
		if\ (pk_{B_{l}} \notin tumblers[j].keys_{B})\ return \ \bot \\
		tx\stackrel{\$}{\leftarrow}Deposit(sk_{A_{i}},pk_{B_{l}}) \\
		H_{w}=H_{w}.push(j,l,tx) \\
		ProcessWithdraw(tumblers[j],tx)\\
		\pcreturn tx }
\end{minipage}
\end{tabular}
\end{table}

From now on, we will denote a specific key in a given session as as $tumbler.keys_{B}$.

@@

\begin{definition}
	Define $\textbf{Adv}^{d-anon}_{mix,\adv}(\lambda) = 2\Pr[\textsf{G}^{d-anon}_{mix,\adv}(\lambda)]-1\ for\ d \in \{dep, with\}$, where these games are defined as follows:

	\begin{table}[H]
		\centering
		\begin{tabular}{cc}    
			\begin{minipage}{7cm}
					\procedure{MAIN $\textsf{G}^{dep-anon}_{mix,\adv}(\lambda)$}{%
						(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
						\textsf{PK}_A\leftarrow\{pk_i\}^{n}_{i=1};C,H_{d}, tumblers \leftarrow \emptyset\\
						b \stackrel{\$}{\leftarrow} \bin \\
						(state,j,pk, i_{0},i_{1}) \stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW} (1^\lambda, \textsf{PK}_{A}) \\
						tx \stackrel{\$}{\leftarrow} Deposit(tumblers[j], sk_{A_{{l}_{b}}}, pk) \\
						b^{’}\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW}(state, tx) \\
						\pcreturn b = b^{’} }
			\end{minipage}
			&
			\begin{minipage}{7cm}
				\procedure{MAIN $\textsf{G}^{with-anon}_{mix,\adv}(\lambda)$}{%
					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{d}, tumblers \leftarrow \emptyset\\
					b \stackrel{\$}{\leftarrow} \bin \\
					(state,j,pk, l_{0},l_{1}) \stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW} (1^\lambda, \textsf{PK}_{B}) \\
					\textsf{PK}\leftarrow tumblers[j].keys_{B}\\
					if(pk_{B_{l_{0}}}\notin \textsf{PK})\lor(pk_{B_{l_{1}}}\notin \textsf{PK})\ return\ 0\\
					tx \stackrel{\$}{\leftarrow} Withdraw(tumblers[j], sk_{B_{{l}_{b}}}) \\
					b^{’}\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HD,AW}(state, tx) \\
					if(pk_{l_{b}}\in C \ for\ b \in \bin)\ return\ 0 \\
					if((j,l_{b},\cdot))\in H_{w} \ for\ b \in \bin)\ return\ 0\\
					\pcreturn b = b^{’} }		
			\end{minipage}
		\end{tabular}
	\end{table}	
Then the tumbler satisfies sender or recipient anonymity if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{dep-anon}_{mix,\adv}(\lambda) < \nu(\lambda)$ or $\textbf{Adv}^{with-anon}_{mix,\adv}(\lambda) < \nu(\lambda)$ respectively.	
\end{definition}

@@

\begin{definition}
	Define $\textbf{Adv}^{avail}_{mix,\adv}(\lambda) = \Pr[\textsf{G}^{avail}_{mix,\adv}(\lambda)]$, where the game is defined as follows:

	\begin{table}[H]
		\centering
		\begin{tabular}{c}    
			\begin{minipage}{7cm}
				\procedure{MAIN $\textsf{G}^{avail}_{mix,\adv}(\lambda)$}{%
					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{w} \leftarrow \emptyset\\
					(l,j)\stackrel{\$}{\leftarrow} \adv^{CORR,AD,HW,AW}(1^{\lambda},\textsf{PK}_{B}) \\
					b \leftarrow  \textsf{VerifyWithdraw}(\textsf{tumblers}[j], \textsf{Withdraw}(sk_{l})) \\
					if ((pk_{l}\in C)\ \lor\ ((j,l,\cdot)\in H_{w}))\ return \ 0 \\
					\pcreturn (b=0)\land(pk_{l}\in tumblers[j].keys_{B})}
			\end{minipage}
		\end{tabular}
	\end{table}	
	Then the tumbler satisfies availability if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{avail}_{mix,\adv}(\lambda) < \nu(\lambda)$.
\end{definition}

\subsubsection{Theft prevention} \label{sec:theftprevention}
We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient. Theft prevention is defined formally as follows:

\begin{definition}
	Define $\textbf{Adv}^{theft}_{mix,\adv}(\lambda) = \Pr[\textsf{G}^{theft}_{mix,\adv}(\lambda)]$, where the game is defined as follows:

	\begin{table}[H]
		\centering
		\begin{tabular}{c}    
			\begin{minipage}{7cm}
				\procedure{MAIN $\textsf{G}^{theft}_{mix,\adv}(\lambda)$}{%
					(pk_{i},sk_{i})\stackrel{\$}{\leftarrow}\kgen(1^{\lambda}) \ \forall i \in [n]\\
					\textsf{PK}_B\leftarrow\{pk_i\}^{n}_{i=1};C,H_{w}, \textsf{contract} \leftarrow \emptyset\\
					(\textsf{tx},j)\stackrel{\$}{\leftarrow} \adv^{CORR,AD,AW,HW}(1^{\lambda},\textsf{PK}_{B}) \\
					if(\textsf{tumblers}[j].\textsf{keys}_{B}\not\subset \textsf{PK}_{B}\setminus C)\ return \ 0 \\
					\pcreturn \textsf{VerifyWithdraw}(\textsf{tumblers}[j], \textsf{tx})}
			\end{minipage}
		\end{tabular}
	\end{table}	
	Then the tumbler satisfies theft prevention if for all PT adversaries $\adv$ there exists a negligible function $\nu(\cdot)$ such that $\textbf{Adv}^{theft}_{mix,\adv}(\lambda) < \nu(\lambda)$.
\end{definition}

@@

\subsection{MixEth formal specification}

\begin{table}[H]
	\centering
	\begin{tabular}{cccc}    
		\begin{minipage}{5.5cm}
			\procedure{\textsf{Deposit}($sk_A, pk_{B}$)}{%
				\pcreturn \textsf{FormTx}(sk_A,id_{\textsf{contract}}, amt, pk_{B}) }
		\end{minipage}
		&
		\begin{minipage}{5.4cm}
			\procedure{\textsf{VerifyDeposit}(tx)}{%
				if\ (tx[amt] \neq id_{\textsf{contract}}[amt]) \ return\ 0 \\
				if\ (pk_{B} \notin \mathbb{G}) \ return\ 0 \\
				\pcreturn \textsf{VerifyTx(tx)}  }
		\end{minipage}
		&
		\begin{minipage}{4cm}
			\procedure{\textsf{ProcessDeposit(tx)}}{%
				add\ \textsf{addr(tx[pk]) to initPubKeys[]}}
		\end{minipage}
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{cccc}    
		\begin{minipage}{5cm}
			\procedure{\textsf{Shuffle($PK,C^{*}$)}}{%
				c\stackrel{\$}{\leftarrow}\mathbb{Z}_{|\mathbb{G}|} \\
				C^{'*} \leftarrow cC^{*} \\
				PK^{'} = \{pk^{'}_{i}|pk^{'}_{i}=c*pk_{i} \forall i \in [1..n]\} \\
				\pcreturn (PK^{'},C^{'*}) }
		\end{minipage}
		&
		\begin{minipage}{5.7cm}
			\procedure{\textsf{UploadShuffle($sk_{A},PK,C^{*}$)}}{%
				\pcreturn \textsf{FormTx}(sk_{A},id_{contract},(PK,C^{*})) }
		\end{minipage}
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{ccc}
		\begin{minipage}{6.3cm}
			\procedure{\textsf{Challenge}($proof_{ChP}(C^{*},sC^{*},C^{'*},sC^{'*}),PK, PK^{'}$)}{%
				if\ (\lnot Verify(proof_{ChP}) ) \ return\ 0 \\
				if\ (sC^{*} \notin PK) \ return\ 0 \\
				delete (C^{'},PK^{'})\\
				slashDeposit(shuffler(C^{'},PK^{'}))\\
				\pcreturn 1  }
		\end{minipage}
		&
		\begin{minipage}{4.6cm}
			\procedure{\textsf{WithdrawShufflingDeposit($sk_{A}$)}}{%
				\pcreturn \textsf{FormTx($sk_{A}, id_{contract},0$)} }
		\end{minipage}
		&
		\begin{minipage}{4.6cm}
			\procedure{\textsf{VerifyWithdrawShufflingDeposit($pk_{A}$)}}{%
				\pcreturn shufflingDepositSlashed(pk_{A}) }
		\end{minipage}
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{cccc}    
		\begin{minipage}{4.7cm}
			\procedure{\textsf{Withdraw($s,C^{*}$)}}{%
				\sigma \leftarrow \sig(C^{*},s, sC^{*}||msg.sender) \\
				\pcreturn \textsf{FormTx($s,C^{*}, id_{\textsf{contract}, 0}, \sigma$)} }
		\end{minipage}
		&
		\begin{minipage}{6.3cm}
			\procedure{\textsf{VerifyWithdraw(tx)}}{%
				if\ (sC^{*} \notin id_{\textsf{contract}}[lastShuffle] ) \ return\ 0 \\
				if\ (\lnot\verify(C^{*}, sC^{*},\sigma, sC^{*}||tx.sender)) \ return\ 0 \\
				\pcreturn \textsf{VerifyTx(tx)}  }
		\end{minipage}
		&
		\begin{minipage}{4cm}
			\procedure{\textsf{ProcessWithdraw(tx)})}{%
				delete\ sC^{*} from\ id_{\textsf{contract}}[lastShuffle]   \\
				tx^{'}\stackrel{\$}{\leftarrow} \textsf{FormTx}(id_{contract}, tx.sender, amt) }
		\end{minipage}
	\end{tabular}
\end{table}

\section{Security}
This section provides informal ideas to the security proofs for the notions of security introduced in Section \ref{securitygoals}. Formal reductions are enclosed in the Appendices.

\subsection{Recipient anonymity}
The withdrawing transaction for recipient $B$ sends funds to the public key $s_{B}C^{*}$. This public key does not reveal any links to the original $s_{B}G$ in case if at least one honest sender shuffled and the DDH assumption holds. Adversary can only distinguish between honest recipients public keys with negligible probability. See reduction proof in Appendix \ref*{appendanon}.
\subsection{Availability}
If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary $\adv$ either breaks the completeness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to honest Ethereum peers.
\subsection{Theft prevention} 
If an adversary is able to steal funds from other users than it would imply that they managed to create a valid message/signature, $(m,\sigma)$ pair for the final shuffled public key of an honest recipient without having access to the secret key of the honest recipient. This contradicts to the assumption that ECDSA is existentially unforgeable. Reduction proof is enclosed in Appendix \ref*{appendtheft}. 
\begin{table}[H] 
	\caption{Security properties achieved by each coin mixing protocol.}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lcccccc@{}}

		\toprule
		\hline
		&\multicolumn{3}{c}{Anonimity against}& \multicolumn{2}{c}{Availability}&Theft prevention\\
		\cline{2-4}\cline{5-6}&outsiders&senders&recipients&sender&tumbler\\
		\hline
		\midrule
		\textbf{Centralized} & & \\
		\midrule
		Mixcoin \cite{bonneau2014mixcoin} & TTP       & \xmark  &\cmark&\cmark&\xmark&TTP      \\
		Blindcoin \cite{valenta2015blindcoin} & \cmark &\xmark&\cmark&\cmark&\xmark&TTP        \\
		TumbleBit \cite{heilman2017tumblebit} & \cmark &\cmark&\cmark&\cmark&\xmark&\cmark       \\
		\midrule
		\textbf{Decentralized}      &    &      \\
		\midrule
		Coinjoin \cite{maxwell2013coinjoin} & \cmark   &\xmark&\cmark&\xmark&n.a.&\cmark       \\
		Coinshuffle \cite{ruffing2014coinshuffle} & \cmark&\xmark&\cmark&\xmark&n.a.&\cmark       \\
		XIM \cite{bissias2014sybil} & \cmark      &\xmark&\cmark&\cmark&n.a.&\cmark       \\
		Möbius \cite{meiklejohn2018mobius}     &\cmark&\cmark&\xmark&\cmark&\cmark&\xmark        \\
		Miximus \cite{miximus2018}&\cmark&\xmark&\xmark&\cmark&\cmark&\cmark  \\
		MixEth&\cmark&\cmark&\xmark&\cmark&\cmark&\cmark  \\
		\bottomrule
	\end{tabular}
	\label{table:securityproperties}
\end{table}

@@

All MixEth smart contracts were written in the Solidity language, which is currently the dominant language for developing Ethereum smart contracts. MixEth contracts are compiled using the latest version of the Solidity compiler in order to take advantage of the latest language features such as the possibility to return dynamic-sized arrays from contract functions. Note that these implementations are only proof-of-concept implementations, expect further improvements. All MixEth contracts are available online\footnote{https://github.com/seresistvanandras/MixEth}.  
\newpage
\subsection{Fully on-chain implementation} \label{fullyonchainimpl}

@@

\newpage
\subsection{State channel implementation} \label{statechannelimpl}

@@

\section{Related work}
Möbius was the very first trustless coin mixer designed for Ethereum\cite{meiklejohn2018mobius}. Authors of Möbius provided formal definitions of various notions of security such as anonymity, theft prevention and mixer availability. These properties could be used to evaluate and compare existing and future proposals from a security perspective. Möbius is a ring-signature-based trustless coin mixer with minimal on-chain transaction complexity: users of Möbius just need to create a deposit and a withdraw transaction. However the gas cost of the withdrawal transaction increases linearly in the number of receivers, which limits the size of possible anonymity sets. No more than 24 reciever could use Möbius with current cca.$\num[group-separator={,}]{8000000}$  block gas limit. If more people tries to use the mixer funds would be stucked in the mixer contract, since the gas costs of withdrawal transactions would be greater than the block gas limit. Another, maybe even more severe problem with Möbius' implementation is that withdrawal transactions can be frontrunned by anyone in the network, meaning that anyone could steal receivers' funds from the Möbius smart contract. When an honest receiver broadcasts a Möbius withdrawal transaction, other peers in the network might just create another withdrawal transaction with the very same valid linkable ring signature but with a considerably larger gas price and with their own address as recipient. Miners will act rationally and pick the transaction with the higher gas price, therefore theft-prevention in Möbius' implementation is not guaranteed.

Miximus is a trustless zkSNARK-based mixer for Ethereum\cite{miximus2018}. It uses zkSNARKs to conceal the mapping between depositors and recipients. A depositor creates a leaf in a Merkle-tree. A depositor needs to exchange the preimage of the leaf with the recipient. Later, a recipient could prove to the Miximus contract that they know one of the preimages of a certain, undisclosed leaf. So called nullifiers enable recipients to withdraw funds once and only once. The gas costs of depositing and withdrawing funds from a Miximus mixer is independent of the number of participants. However there are disadvantages of this approach; Miximus only provides anonymity against outsiders, since if Alice funds to Bob via Miximus, Alice will know when Bob made the withdrawal transaction. Another, more severe limitation of Miximus is the trusted setup required for generating the proving key for the zkSNARK. If this trusted setup is compromised, the deployer of the contract, who generated the proving key could potentially steal funds from the mixer. Although, this issue could be amended somehow via a multi-party computation (MPC) further increasing the off-chain communication complexitiy of Miximus.

As Table \ref{table:communicationcomplexity} demonstrates, both Möbius and Miximus require $2$ on-chain transactions, while MixEth requires $3$. In spite of this seemingly added complexity, the 3 on-chain transactions to complete the MixEth protocol (deposit, shuffle, withdraw) consume significantly less gas than those (deposit, verify linkable ring signature/zkSNARK) of Möbius and Miximus, see Table~\ref{table:gasproperties}. 
\begin{table}[H] 
\caption{Number of on-chain transactions and off-chain messages per a single participant required to run a certain coin mixer protocol. Note that in case of Miximus if one wants to avoid the trusted setup for the zkSNARK, then they need to perform a secure multi-party computation protocol to trust-minimize the proving key generation.}
\centering 
\begin{tabular}{lcc}

	\toprule
	&\#Off-chain messages& \#Transactions \\
	\midrule
	\textbf{Centralized} & & \\
	\midrule
	Mixcoin \cite{bonneau2014mixcoin} & 2      & 2       \\
	Blindcoin \cite{valenta2015blindcoin} & 4      & 2       \\
	TumbleBit \cite{heilman2017tumblebit} & 12      & 4      \\
	\midrule
	\textbf{Decentralized}      &    &      \\
	\midrule
	Coinjoin \cite{maxwell2013coinjoin} &  $\mathcal{O}(n^2)$     & 1       \\
	Coinshuffle \cite{ruffing2014coinshuffle} &$\mathcal{O}(n)$       & 1       \\
	XIM \cite{bissias2014sybil} & 0      & 7       \\
	Möbius \cite{meiklejohn2018mobius} & 2    & 2       \\
	Miximus \cite{miximus2018} & 1+MPC & 2 \\
	MixEth & 1 & 3 \\
	MixEthChannel  & $\mathcal{O}(n)$ &2 \\
	\bottomrule
\end{tabular}
\label{table:communicationcomplexity}
\end{table}

\subsection{Additional related work}
Recently, in November 26, 2018 a new privacy-enhancing protocol and tool was released, called Aztec protocol \cite{aztecprotocol2018}. Aztec allows its users to convert any type of existing digital asset on top Ethereum into Aztec notes. Later on Aztec notes can be traded in a join-split style confidential transaction, namely the value of the traded Aztec notes are encrypted and not visible to outsiders. A join-split style transaction can have multiple inputs and outputs. Aztec applies zero-knowledge proofs and range proofs in order to achieve that the sum of inputs traded in a confidential transaction is greater or equal than the sum of outputs. The gas cost of a confidential Aztec transaction is $\num[group-separator={,}]{219000}$+$\num[group-separator={,}]{121000}n$+$\num[group-separator={,}]{41000}m$, where $n$ and $m$ are the numbers of inputs and outputs respectively.  Although Aztec is not a coin mixer, it can be used not only to provide confidential transaction, but also to increase anonymity. On the downside Aztec uses a trusted setup and considerably more expensive than MixEth to provide the same level of k-anonymity, however it is able to conceal transaction volumes. Most likely a combination of MixEth and Aztec would yield the most gas-efficient solution to achieve k-anonym and confidential transactions. For instance on top Aztec one could use MixEth to shuffle Aztec notes.

\section{Extensions and improvements}
MixEth is not fully compatible with the current EVM, however it could be deployed with a workaround. A recipient could ask another party or service to send a signed transaction including a signature which uses the modified version of ECDSA, where the generator element is the shuffling accumulated constant. MixEth could check this signature and send out funds to a fresh Ethereum address given in the withdraw transaction.

In the current design of MixEth if sender, Alice and receiver, Bob would like to use the mixer several times, Bob needs to share his receiver address in a secure communication channel with Alice as many times as he would like to receive payments. This communication overhead could be overcome by applying stealth addresses, where Bob needs to share once his public master key with Alice in order to receive arbirtary number of payments from her.

\section{Conclusion and Future Work} \label{conclusion}
We are going to conduct external code audits, deploy MixEth on the Ethereum main net and evaluate its performance. An important and crucial research question is whether it is possible to design and implement an efficient and trustless Ethereum-based coin mixer with strong security guarantees which do not rely on any workaround or upcoming EIP implementation and is ready to be deployed on present-day Ethereum.

@@

\begin{appendices}

\section{Proof of Anonymity} \label{appendanon}
Hereby we show that if there exists an adversary $\adv$ who is able to break withdrawal anonymity defined in~\ref{sec:defanonymity}, then there exists another adversary $\bdv$ who is able to break the DDH assumption.

>>>>

@@

@@

\section{Background}
\subsection{Notations}
In most cases if it is possible we will stick to the notations used in \cite{meiklejohn2018mobius} for sake of uniformity. 
Let $[]$ denote the empty tuple. For a tuple $t=(x_1,\dots,x_n)$ we denote as $t[x_i]$ the value stored at $x_{i}$. The cardinality of a finite set $X$ is denoted as $|X|$. In the following let $\lambda \in \mathbb{N}$ be the security parameter and its unary representation is $1^{\lambda}$. If $x$ is uniformly randomly sampled from a set $A$ we write $x\stackrel{\$}{\leftarrow}A$. The symmetric group of degree $n$ is written as ${S}_n$. In a cyclic group $\mathbb{G}$, the standardized generator is denoted as $G$ and we use the additive notation. Secret keys and public keys are denoted as $sk$ and $pk$ respectively (or often times $s$ and $sG$), while the user the corresponding key belongs to is indicated in subscript. Let $PK_{i}$ denote the set of public keys belonging to receivers at a particular shuffling round $i$.

@@

@@

@@

@@

\section{Security goals} \label{securitygoals}
We are aiming to achieve and prove the same notions of security as the ones defined in \cite{meiklejohn2018mobius}, namely anonymity, availability and theft prevention. These notions of anonymity, availability and theft prevention were introduced in \cite{meiklejohn2018mobius}.

@@

@@

@@

\subsubsection{Theft prevention} \label{sec:theftprevention}
We would like to ensure that neither coins can be withdrawn twice, nor withdrawn by anyone other but the intended recipient.

@@

\section{Informal reasoning about security properties}

\subsection{Recipient anonymity}
The withdrawing transaction for recipient $B$ sends funds to the public key $s_{B}C^{*}$. This public key does not reveal any links to the original $s_{B}G$ in case if at least one honest sender shuffled and the DDH assumption holds. Adversary can only distinguish between honest recipients public keys with negligible probability. See reduction proof in Appendix \ref*{appendanon}.
\subsection{Availability}
If an adversary is able to destroy an honest recipient's funds' availability, it implies that adversary $\adv$ either breaks the completeness of the Chaum-Pedersen protocol or successfully launched an eclipse attack against the honest recipient, who can not send any transactions to honest Ethereum peers.
\subsection{Theft prevention} 
If an adversary is able to steal funds from other users than it would imply that they managed to create a valid message/signature, $(m,\sigma)$ pair for the final shuffled public key of an honest recipient without having access to the secret key of the honest recipient. This contradicts to the assumption that ECDSA is existentially unforgeable. Reduction proof is enclosed in Appendix \ref*{appendtheft}.

@@

All MixEth smart contracts were written in the Solidity language, which is currently the dominant language for developing Ethereum smart contracts. MixEth contracts are compiled using the latest version of the Solidity compiler in order to take advantage of the latest language features such as the possibility to return dynamic-sized arrays from contract functions. Note that these implementations are only proof-of-concept implementations, expect further improvements. All MixEth contracts are available online\footnote{https://github.com/seresistvanandras/MixEth}.

\subsection{Fully on-chain implementation} \label{fullyonchainimpl}

@@

\subsection{State channel implementation} \label{statechannelimpl}

@@

@@
